Centralizers of higher enveloping algebras of Lie algebras

### 2020-08-31 draft.tex
rearrangements

@@

\subsection{End of the proof}
Combining the result of the last two sections we obtain immediately the following factorization algebra model for our main theorem:
\begin{thm}\label{thm:centralizerfactorization}
Let $k$ be $\RR$ or $\CC$, and assume $\mathbf{f}:  \UU_n \fg \to B(-)$ is a map of augmented factorization algebras. 
Then, the centralizer ${\frak Z}(\mathbf{f})$ is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), B(U))
\]
to each open set $U \subset \RR^n$. 
\end{thm}
\begin{proof}
 In section~\ref{SS:constuctionthetaf}, we have constructed a factorization algebra map 
 $\theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)$. Proposition~\ref{L:canonicaltocenterisquis} 
 states that this map is an equivalence he Chevalley-Eilenberg factorization algebra cochains and the factorization algebra center of $f$ as claimed.
\end{proof}
By Lurie's equivalence (Theorem~\ref{T:En=Fac}) between the $\infty$-categories of $E_n$-algebras and locally constant factorization algebras 
over $\RR^n$ (and the last part of lemma~\ref{L:thetaquisondisk}),
the main theorem~\ref{thm: centralizer} follows from its factorization algebra counterpart~\ref{thm:centralizerfactorization}, 
that is from Theorem~\ref{thm:centerfactorization}. This proves the theorem over $k=\RR$ (or $\CC$).

@@

Corollary~\ref{cor:centerfactorization}  is a consequence of theorem~\ref{thm:centralizerfactorization} obtained from applyting the universal 
$E_n$-enveloping algebra functor to a (homotopy) Lie algebra homorphism.

@@

\section{Factorization algebra description of the center}\label{S:centerinFacAlg}
The universal property of centralizer (definition~\ref{D:centralizer}) implies that, for any $E_n$-algebras maps $A\stackrel{f}\to B$ and
$B\stackrel{g}\to C$, there are natural morphisms
\begin{equation}\label{eqdef:canonicaltocentralizers} {\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f)
\end{equation}

in the $\infty$-catgeory of $E_n$-algebras which are given by the  
following commutative diagrams of $E_n$-algebras:
\[\begin{tikzcd}
&   {\frak Z}_{E_n}(g) \otimes  {\frak Z}_{E_n}(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_{E_n}(g) \otimes  B \arrow[dr, "\ev_g"]\\
A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C. 
\end{tikzcd}\]
 When $f=g=\id_A:A\to A$, we obtain a canonical morphism \begin{equation} \label{eq:dgAssofcenter}
 {\frak Z}_{E_n}(A){\otimes} {\frak Z}_{E_n}(A) \longrightarrow {\frak Z}_{E_n}(A).\end{equation}
 Lurie has proved that this multiplication makes the center into an (homotopy) dg-associative algebras in $E_n$-algebras 
 and therefore an $E_{n+1}$-algebra. Precisely: 
\begin{prp}[\cite{LurieHA} Section 5] \label{P:PtyCenter}
\begin{itemize}
 \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_{E_n}(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
 $E_n$-algebras.
 \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(E_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
\end{itemize}
\end{prp}
When $A(-)$ is a factorization algebra model for $A$, in virtue of theorem~\ref{T:En=Fac} 
(and \greg{add reference for fac algebra in fac algebra maybe too}), in order to have a factorization algebra 
model of the center of $A$, it is sufficient to describe the induced map 
\[{\frak Z}(A(-)){\otimes} {\frak Z}(A(-)) \longrightarrow {\frak Z}(A(-))\]
as a factorization algebra homomorphism which makes it an associative object in the category of locally constant factorization algebras.

We now turn to the specific case   of enveloping algebras $\UU_n(\fg)$.

Let $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms; for instance a dg-Lie algebras morphisms. We write 
\[ \mathbf{f}:\cliels\big(\fg \otimes \Omega^*_c(-)\big) \to  \cliels\big(\fh \otimes \Omega^*_c(-)\big), \quad 
\mathbf{h}:\cliels\big(\fh \otimes \Omega^*_c(-)\big) \to  \cliels\big(\fl \otimes \Omega^*_c(-)\big)\]
for the induced morphisms on their enveloping factorization algebras over $\RR^n$.

The inclusion  of compactly supported forms on all forms induces, for any open $U$,  the  map
\begin{equation}
 \label{eq:incofcpctforms} 
\iota_U: \cliels\big(\fh \otimes \Omega^*_c(U)\big) \, \cong \, 
Sym\big( \fh\otimes  \Omega^*_c (U) [1]\big) \hookrightarrow  
Sym\big( \fh\otimes  \Omega^* (U) [1]\big).
\end{equation}
Recall from section~\ref{SS:constuctionthetaf} that the Chevalley Eilenberg cochain factorization algebras (with values in an augmented factorization 
algebras) 
are canonically pointed  by $\mathbf{1}\in \clies(\fg\otimes \Omega^*(-), B(-)) )$ which is induced by 
the unit $k(-)\to \clies(\fg\otimes \Omega^*(-), B(-)) )$
 of the factorization structures.  In particular, we have the canonical splitting~\eqref{eq:splittingbyaugm} 
of the  Chevalley-Eilenberg cochain factorization algebras, and an associated grading~\eqref{eq:defgraduationoncentralizernonconnected2} on each open
set. We denote $\varphi= \lambda_\varphi +\overline{\varphi}$ the induced decomposition given by the splitting~\eqref{eq:splittingbyaugm} . 
We use these gradings as in section~\ref{SS:constuctionthetaf} to construct a composition as follows. 
\begin{dfn}\label{def:comp}
For any \emph{connected} open set $W$, we define  the composition 
$$\clies\big(\fh \otimes \Omega(W), \cliels(\fl \otimes \Omega_c(W)  \big) \otimes 
\clie\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)
\stackrel{(-\star-)}\longrightarrow 
\clies\big(\fg \otimes \Omega(W), \cliels(\fl \otimes \Omega_c(W)  \big)
$$ to be given, for any $$\psi=\lambda_\psi \mathbf{1} +\overline{\psi} \in \clies\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)=
\Hom(Sym\big( \fh\otimes  \Omega (W) [1]\big), Sym\big( \fl\otimes  \Omega_c (W) [1]\big))$$
$$\mbox{and }\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}\in \clies\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)= 
\Hom(Sym\big( \fg\otimes  \Omega (W) [1]\big), Sym\big( \fh\otimes  \Omega_c (W) [1]\big)) $$ by 
$$ \psi \star \varphi \, := \, \lambda_{\psi} \lambda_{\varphi} \mathbf{1}+
\lambda_\psi g\circ \overline{\varphi} + \lambda_{\varphi} \overline{\psi} \circ \iota_W \circ f +\overline{\psi} \circ \iota_U \circ \overline{\varphi} . $$
For any open 
$U=\coprod\limits_{i\in I}U_i$, where the $U_i$ are the connected components of $U$,  we define  the composition 
$$\clies\big(\fh \otimes \Omega(U), \cliels(\fl \otimes \Omega_c(U)  \big) \otimes 
\clie\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)
\stackrel{(-\star-)}\longrightarrow 
\clies\big(\fg \otimes \Omega(U), \cliels(\fl \otimes \Omega_c(U)  \big)
$$ as follows. For any $$\psi \in \clies\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)=
\Hom(Sym\big( \fh\otimes  \Omega (U) [1]\big), Sym\big( \fl\otimes  \Omega_c (U) [1]\big))$$
$$\mbox{and }\varphi \in \clies\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)= 
\Hom(Sym\big( \fg\otimes  \Omega (U) [1]\big), Sym\big( \fh\otimes  \Omega_c (U) [1]\big)), $$ we write 
$\varphi = \mathop{\bigotimes}\limits_{i\in I} \varphi_i$, $\psi= \mathop{\bigotimes}\limits_{i\in I} \psi_i$ 
(where $\varphi_i \in \clies\big(\fg \otimes \Omega(U_i), \cliels(\fh \otimes \Omega_c(U_i)  \big)$,
$\psi_i\in \clies\big(\fh \otimes \Omega(U_i), \cliels(\fl \otimes \Omega_c(U_i)  \big)$) 
 using the decomposition~\eqref{eq:defgraduationoncentralizernonconnected}. Then we define
\begin{equation} \label{eqdef:staronnonconnected}
\psi \star \varphi \, := \mu_{\fl} \circ \Big( \bigotimes\limits_{i\in I} (\psi_i \star \varphi_i)\Big) \end{equation}
where $\mu_{\fl}: \mathop{\bigotimes}\limits_{i\in I} \cliels(\fl\otimes \Omega^c(U_I)) \cong \cliels(\fl\otimes \Omega^c(U))$ 
is given by the factorization algebra 
structure. 
\end{dfn}
Since $\iota_U$ is an embeding for every $U$, in the rest of the paper, we will usually 
omit it in the formulas.

\begin{lmm}\label{L:compisfacmap} The composition $$\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) \otimes 
\clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big)
\stackrel{(-\star-)}\longrightarrow 
\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)
$$
 is a morphism of factorization algebras.
\end{lmm}
\begin{proof}

\end{proof}
The composition is compatible with the augmentation splitting. Precisely, we have
\begin{lmm}\label{L:compisaugmented} For any $\varphi \in \clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big)$,
$\psi \in \clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)$
 One has the following equalities  :
 \begin{align}
  \overline{\psi\star \varphi} \;= \;\mathbf{1}\star \overline{\varphi} +\overline{\psi}\star \mathbf{1} +\overline{\psi}\star \overline{\varphi} 
  & \quad\mbox{ (in  $\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $)}\\
 \mathbf{1}\star \varphi \;=\;  (\lambda_\varphi \mathbf{1}, g\circ \overline{\varphi})\qquad
  &\quad\mbox{ (in  $k(-)  \oplus \overline{\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)}$)}\\
  \psi \star \mathbf{1}\;=\; (\lambda_\psi \mathbf{1}, \overline{\psi} \circ f) \qquad
  &\quad\mbox{ (in  $k(-)  \oplus \overline{\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)}$).}
 \end{align}
 In particular, $\mathbf{1} \star \mathbf{1} =\mathbf{1}$.
\end{lmm}
\greg{maybe I shoudl use the notation $\mathbf{1}_{\mathbf{f}}$, $\mathbf{1}_{\mathbf{g}}$, $\mathbf{1}_{\mathbf{g\circ f}}$ to differentiate 
the various spaces in which leaves the units and avoid possible confusion...?}
\begin{proof}

\end{proof}
The composition is asscoiative in the following sense.
\begin{lmm}\label{L:compisassociative} Let $\fg \stackrel{f}\to \fh$, $\fh \stackrel{g}\to \fl$ and $\fl \stackrel{h}\to \fk$ be maps of $L_\infty$-algebras.
 Then, we have, for any $\varphi \in \clies\big(\fg\otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)) \big)$, 
  $\psi \in \clies\big(\fh\otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)) \big)$ and  
  $\gamma \in \clies\big(\fl\otimes \Omega(-), \cliels(\fk \otimes \Omega_c(-)) \big)$, the equality 
  \[ (\gamma\star \psi)\star \varphi \;=\; \gamma\star (\psi \star \varphi) \quad \mbox{ in 
  $\clies\big(\fg\otimes \Omega(-), \cliels(\fk \otimes \Omega_c(-)) \big)$.}  \]
\end{lmm}
\begin{proof}

\end{proof}

\begin{lmm}\label{L:NatPptyofComp}
 The following diagram of factorization algebras 
 \[\tiny \begin{tikzcd}
 \clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
 \otimes  \clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big) 
 \otimes \cliels(\fg \otimes \Omega_c(-)  \big) \arrow[rd, "(-\star-)\otimes \id"]
 \arrow[dd, "\id\otimes \ev_ {\mathbf{f}}"]& \\ 
 & \clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
 \otimes \cliels(\fg \otimes \Omega_c(-)  \big)
 \arrow[dd, "\ev_{\mathbf{g}\circ \mathbf{f}}"]\\
\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
 \otimes \cliels(\fh \otimes \Omega_c(-)  \big)  \arrow[rd, "\ev_{\mathbf{g}}"] & \\  & \cliels(\fl \otimes \Omega_c(-)  \big). 
\end{tikzcd}\]
 is commutative.
\end{lmm}
\begin{proof}

\end{proof}

>>>>

\owen{Discussion of convolution fact algs commented out below}
%
%To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
%we can associate its Chevalley-Eilenberg cochain complex defined 
%by 
%\begin{equation}
% \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
%\end{equation}
%with its classical differential. 
%\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
%We have the evaluation map 
%\begin{equation}
% \label{eq:defev} ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
%\end{equation}
%given by applying a function on a given tensor in $Sym(\fg[-1])$.
%
%\begin{dfn}\label{D:convolutionalgebraCE}Let $\fg$ be a dg Lie (or $L_\infty$)-algebra and $B$ be an $E_n$-algebra in $\fg$-modules,
%that is an object of the $\infty$-category 
%$E_n-Alg(Mod_{\fg})$. Its associated convolution $E_n$-algebra structure on  $\clies(\fg, B) = \Hom (Sym(\fg[-1]), B)$ is obtained by 
% taking the \emph{convolution} between the cocommutative symmetric coalgebra $Sym(\fg[-1])$ (forgetted to an $E_n$-coalgebra) and the $E_n$-algebra $B$.
%\end{dfn}
%\greg{Probably need somewhere to say what means $E_n-Alg(Mod_{\fg})$ and find a less ugly notation for it}
%Precisely, given an explicit $E_n$-operad $D_n$ in chain complexes and $(B, \mu^B)$ a $D_n$-algebra, 
%the convolution structure is given by the following composition
%\begin{multline}
% \Big(D_n(r)\otimes \clies(\fg, B)^{\otimes r} \Big)\otimes Sym(\fg[-1])\\ \stackrel{id\otimes id \otimes\Delta^{(r-1)}}\longrightarrow 
% D_n(r)\otimes \clies(\fg, B)^{\otimes r} \otimes Sym(\fg[-1])^{\otimes r} 
% \stackrel{id \otimes (ev^{\otimes r})}\longrightarrow D_n(r)\otimes B^{\otimes r} 
% \stackrel{\mu_\sigma^B}\longrightarrow B.
%\end{multline}
%where $\Delta$ is the cocommutative comultiplication.
%In plain formula,
%for any $\sigma \in D_n(r)$ and $\phi_1,\dots, \phi_r \in 
%\clies(\fg, B)$, their multiplication (parametrized by $\sigma$) is  given by 
%\begin{equation}
% \mu_\sigma (\phi_1,\dots, \phi_r): Sym(\fg[-1]) \ni x \mapsto \pm \mu^B_{\sigma} \big(\phi_1(x^{(1)}), \dots, \phi_r(x^{(r)})\big)
%\end{equation}
%where $x\mapsto x^{(1)}\otimes \cdots x^{(r)}$ is the usual $r$-fold cocommutative comultiplication.
%Note that here, we are using the usual Koszul sign  convention. 
%
%\begin{lmm}
% $\clies(\fg, M) = \Hom (Sym(\fg[-1]), B)$ is a $E_n$-algebra, naturally in $\fg$ and $B$.
%\end{lmm}

@@

\subsection{End of the proof}

Combining the result of the last two sections we obtain immediately the following factorization algebra model for our main theorem:
\begin{thm}\label{thm:centralizerfactorization}
Let $k$ be $\RR$ or $\CC$, and assume $\mathbf{f}:  \UU_n \fg \to B(-)$ is a map of augmented factorization algebras. 
Then, the centralizer ${\frak Z}(\mathbf{f})$ is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), B(U))
\]
to each open set $U \subset \RR^n$. 
\end{thm}
\begin{proof}
 In section~\ref{SS:constuctionthetaf}, we have constructed a factorization algebra map 
 $\theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)$. Proposition~\ref{L:canonicaltocenterisquis} 
 states that this map is an equivalence he Chevalley-Eilenberg factorization algebra cochains and the factorization algebra center of $f$ as claimed.
\end{proof}

By Lurie's equivalence (Theorem~\ref{T:En=Fac}) between the $\infty$-categories of $E_n$-algebras and locally constant factorization algebras 
over $\RR^n$ (and the last part of lemma~\ref{L:thetaquisondisk}),
the main theorem~\ref{thm: centralizer} follows from its factorization algebra counterpart~\ref{thm:centralizerfactorization}, 
that is from Theorem~\ref{thm:centerfactorization}. This proves the theorem over $k=\RR$ (or $\CC$).

@@

Corollary~\ref{cor:centerfactorization}  is a consequence of theorem~\ref{thm:centralizerfactorization} obtained from applyting the universal 
$E_n$-enveloping algebra functor to a (homotopy) Lie algebra homomorphism.

@@

\owen{Commented out here is a discussion of centers. We may want to resurrect it but it doesn't seem essential to the main results.}

%\section{Factorization algebra description of the center}
%\label{S:centerinFacAlg}
%The universal property of centralizer (definition~\ref{D:centralizer}) implies that, for any $E_n$-algebras maps $A\stackrel{f}\to B$ and
%$B\stackrel{g}\to C$, there are natural morphisms
%\begin{equation}\label{eqdef:canonicaltocentralizers} {\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f)
%in the $\infty$-catgeory of $E_n$-algebras which are given by the  
%following commutative diagrams of $E_n$-algebras:
%\[\begin{tikzcd}
%&   {\frak Z}_{E_n}(g) \otimes  {\frak Z}_{E_n}(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_{E_n}(g) \otimes  B \arrow[dr, "\ev_g"]\\
%A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C. 
%\end{tikzcd}\]
% When $f=g=\id_A:A\to A$, we obtain a canonical morphism \begin{equation} \label{eq:dgAssofcenter}
% {\frak Z}_{E_n}(A){\otimes} {\frak Z}_{E_n}(A) \longrightarrow {\frak Z}_{E_n}(A).\end{equation}
% Lurie has proved that this multiplication makes the center into an (homotopy) dg-associative algebras in $E_n$-algebras 
% and therefore an $E_{n+1}$-algebra. Precisely: 
%\begin{prp}[\cite{LurieHA} Section 5] \label{P:PtyCenter}
%\begin{itemize}
% \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_{E_n}(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
% $E_n$-algebras.
% \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(E_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
%\end{itemize}
%When $A(-)$ is a factorization algebra model for $A$, in virtue of theorem~\ref{T:En=Fac} 
%(and \greg{add reference for fac algebra in fac algebra maybe too}), in order to have a factorization algebra 
%model of the center of $A$, it is sufficient to describe the induced map 
%\[{\frak Z}(A(-)){\otimes} {\frak Z}(A(-)) \longrightarrow {\frak Z}(A(-))\]
%as a factorization algebra homomorphism which makes it an associative object in the category of locally constant factorization algebras.
%We now turn to the specific case   of enveloping algebras $\UU_n(\fg)$.
%Let $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms; for instance a dg-Lie algebras morphisms. We write 
%\[ \mathbf{f}:\cliels\big(\fg \otimes \Omega^*_c(-)\big) \to  \cliels\big(\fh \otimes \Omega^*_c(-)\big), \quad 
%\mathbf{h}:\cliels\big(\fh \otimes \Omega^*_c(-)\big) \to  \cliels\big(\fl \otimes \Omega^*_c(-)\big)\]
%for the induced morphisms on their enveloping factorization algebras over $\RR^n$.
%The inclusion  of compactly supported forms on all forms induces, for any open $U$,  the  map
% \label{eq:incofcpctforms} 
%\iota_U: \cliels\big(\fh \otimes \Omega^*_c(U)\big) \, \cong \, 
%Sym\big( \fh\otimes  \Omega^*_c (U) [1]\big) \hookrightarrow  
%Sym\big( \fh\otimes  \Omega^* (U) [1]\big).
%Recall from section~\ref{SS:constuctionthetaf} that the Chevalley Eilenberg cochain factorization algebras (with values in an augmented factorization 
%algebras) 
%are canonically pointed  by $\mathbf{1}\in \clies(\fg\otimes \Omega^*(-), B(-)) )$ which is induced by 
%the unit $k(-)\to \clies(\fg\otimes \Omega^*(-), B(-)) )$
% of the factorization structures.  In particular, we have the canonical splitting~\eqref{eq:splittingbyaugm} 
%of the  Chevalley-Eilenberg cochain factorization algebras, and an associated grading~\eqref{eq:defgraduationoncentralizernonconnected2} on each open
%set. We denote $\varphi= \lambda_\varphi +\overline{\varphi}$ the induced decomposition given by the splitting~\eqref{eq:splittingbyaugm} . 
%We use these gradings as in section~\ref{SS:constuctionthetaf} to construct a composition as follows. 
%\begin{dfn}\label{def:comp}
%For any \emph{connected} open set $W$, we define  the composition 
%$$\clies\big(\fh \otimes \Omega(W), \cliels(\fl \otimes \Omega_c(W)  \big) \otimes 
%\clie\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)
%\stackrel{(-\star-)}\longrightarrow 
%\clies\big(\fg \otimes \Omega(W), \cliels(\fl \otimes \Omega_c(W)  \big)
%$$ to be given, for any $$\psi=\lambda_\psi \mathbf{1} +\overline{\psi} \in \clies\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)=
%\Hom(Sym\big( \fh\otimes  \Omega (W) [1]\big), Sym\big( \fl\otimes  \Omega_c (W) [1]\big))$$
%$$\mbox{and }\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}\in \clies\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)= 
%\Hom(Sym\big( \fg\otimes  \Omega (W) [1]\big), Sym\big( \fh\otimes  \Omega_c (W) [1]\big)) $$ by 
%$$ \psi \star \varphi \, := \, \lambda_{\psi} \lambda_{\varphi} \mathbf{1}+
%\lambda_\psi g\circ \overline{\varphi} + \lambda_{\varphi} \overline{\psi} \circ \iota_W \circ f +\overline{\psi} \circ \iota_U \circ \overline{\varphi} . $$
%For any open 
%$U=\coprod\limits_{i\in I}U_i$, where the $U_i$ are the connected components of $U$,  we define  the composition 
%$$\clies\big(\fh \otimes \Omega(U), \cliels(\fl \otimes \Omega_c(U)  \big) \otimes 
%\clie\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)
%\stackrel{(-\star-)}\longrightarrow 
%\clies\big(\fg \otimes \Omega(U), \cliels(\fl \otimes \Omega_c(U)  \big)
%$$ as follows. For any $$\psi \in \clies\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)=
%\Hom(Sym\big( \fh\otimes  \Omega (U) [1]\big), Sym\big( \fl\otimes  \Omega_c (U) [1]\big))$$
%$$\mbox{and }\varphi \in \clies\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)= 
%\Hom(Sym\big( \fg\otimes  \Omega (U) [1]\big), Sym\big( \fh\otimes  \Omega_c (U) [1]\big)), $$ we write 
%$\varphi = \mathop{\bigotimes}\limits_{i\in I} \varphi_i$, $\psi= \mathop{\bigotimes}\limits_{i\in I} \psi_i$ 
%(where $\varphi_i \in \clies\big(\fg \otimes \Omega(U_i), \cliels(\fh \otimes \Omega_c(U_i)  \big)$,
%$\psi_i\in \clies\big(\fh \otimes \Omega(U_i), \cliels(\fl \otimes \Omega_c(U_i)  \big)$) 
% using the decomposition~\eqref{eq:defgraduationoncentralizernonconnected}. Then we define
%\begin{equation} \label{eqdef:staronnonconnected}
%\psi \star \varphi \, := \mu_{\fl} \circ \Big( \bigotimes\limits_{i\in I} (\psi_i \star \varphi_i)\Big) \end{equation}
%where $\mu_{\fl}: \mathop{\bigotimes}\limits_{i\in I} \cliels(\fl\otimes \Omega^c(U_I)) \cong \cliels(\fl\otimes \Omega^c(U))$ 
%is given by the factorization algebra 
%structure. 
%Since $\iota_U$ is an embeding for every $U$, in the rest of the paper, we will usually 
%omit it in the formulas. 
%\begin{lmm}\label{L:compisfacmap} The composition $$\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) \otimes 
%\clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big)
%\stackrel{(-\star-)}\longrightarrow 
%\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)
%$$
% is a morphism of factorization algebras.
%The composition is compatible with the augmentation splitting. Precisely, we have
%\begin{lmm}\label{L:compisaugmented} For any $\varphi \in \clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big)$,
%$\psi \in \clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)$
% One has the following equalities  :
% \begin{align}
%  \overline{\psi\star \varphi} \;= \;\mathbf{1}\star \overline{\varphi} +\overline{\psi}\star \mathbf{1} +\overline{\psi}\star \overline{\varphi} 
%  & \quad\mbox{ (in  $\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $)}\\
% \mathbf{1}\star \varphi \;=\;  (\lambda_\varphi \mathbf{1}, g\circ \overline{\varphi})\qquad
%  &\quad\mbox{ (in  $k(-)  \oplus \overline{\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)}$)}\\
%  \psi \star \mathbf{1}\;=\; (\lambda_\psi \mathbf{1}, \overline{\psi} \circ f) \qquad
%  &\quad\mbox{ (in  $k(-)  \oplus \overline{\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)}$).}
% \end{align}
% In particular, $\mathbf{1} \star \mathbf{1} =\mathbf{1}$.
%\greg{maybe I shoudl use the notation $\mathbf{1}_{\mathbf{f}}$, $\mathbf{1}_{\mathbf{g}}$, $\mathbf{1}_{\mathbf{g\circ f}}$ to differentiate 
%the various spaces in which leaves the units and avoid possible confusion...?}
%The composition is asscoiative in the following sense.
%\begin{lmm}\label{L:compisassociative} Let $\fg \stackrel{f}\to \fh$, $\fh \stackrel{g}\to \fl$ and $\fl \stackrel{h}\to \fk$ be maps of $L_\infty$-algebras.
% Then, we have, for any $\varphi \in \clies\big(\fg\otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)) \big)$, 
%  $\psi \in \clies\big(\fh\otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)) \big)$ and  
%  $\gamma \in \clies\big(\fl\otimes \Omega(-), \cliels(\fk \otimes \Omega_c(-)) \big)$, the equality 
%  \[ (\gamma\star \psi)\star \varphi \;=\; \gamma\star (\psi \star \varphi) \quad \mbox{ in 
%  $\clies\big(\fg\otimes \Omega(-), \cliels(\fk \otimes \Omega_c(-)) \big)$.}  \]
%\begin{lmm}\label{L:NatPptyofComp}
% The following diagram of factorization algebras 
% \[\tiny \begin{tikzcd}
% \clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
% \otimes  \clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big) 
% \otimes \cliels(\fg \otimes \Omega_c(-)  \big) \arrow[rd, "(-\star-)\otimes \id"]
% \arrow[dd, "\id\otimes \ev_ {\mathbf{f}}"]& \\ 
% & \clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
% \otimes \cliels(\fg \otimes \Omega_c(-)  \big)
% \arrow[dd, "\ev_{\mathbf{g}\circ \mathbf{f}}"]\\
%\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
% \otimes \cliels(\fh \otimes \Omega_c(-)  \big)  \arrow[rd, "\ev_{\mathbf{g}}"] & \\  & \cliels(\fl \otimes \Omega_c(-)  \big). 
%\end{tikzcd}\]
% is commutative.
%\begin{thm}\label{T:compcentralizer}
% Let $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms.
%\begin{enumerate} \item 
% The composition $(-\star-)$ of factorization algebras (definition~\ref{def:comp}) 
% is the canonical map 
%\[{\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f).\] 
%\item If $f= \fg \stackrel{\id}\to \fg$,  the composition $(-\star-)$ makes 
%$\clies\big(\fg \otimes \Omega(-), \cliels(\fg \otimes \Omega_c(-)) \big)$ into an 
%(augmented) associative algebra object in factorization algebra, with unit given by $\mathbf{1}$, 
%which is equivalent to the structure of the center ${\frak Z} (\cliels(\fg \otimes \Omega_c(-)))$. 
%\end{enumerate}
%\end{thm}
%By universal property of centralizers, the canonical map~\eqref{eqdef:canonicaltocentralizers}  
%is the unique\footnote{it is unique in the $\infty$-categorical 
%sense, that is there is a contractible space of choices for it} map 
%\[ \Upsilon: {\frak Z}_{E_n}(\UU_n g) \otimes {\frak Z}_{E_n}(\UU_n f) \longrightarrow {\frak Z}_{E_n}\big(\UU_n (g\circ f)\big)\] 
%of $E_n$-algebras which makes the following diagram
%\begin{equation}\label{eq:comdiagforcentralizercomput}\small
% \xymatrix{
%&   &&  
%{\frak Z}_{E_n}\big(\UU_n (g\circ f) \big) \otimes  \UU_n \fg  \ar@/^{2pc}/[dddr]^{\ev_{\UU_n (g\circ f)}}\\
%&{\frak Z}_{E_n}(\UU_n g) \otimes  {\frak Z}_{E_n}(\UU_n f) \otimes \UU_n \fg \ar@/^{1pc}/[rru]_{ \Upsilon \otimes \id_{\UU_n \fg}} \ar[rrd]_{\id\otimes \ev_{\UU_n f}}
%&& (1)
%& & \\
%\UU_n \fg \ar[ur]_{1^{\otimes 2}\otimes \id_{\UU_n \fg}} \ar@/_{1pc}/[rrd]^{\UU_n f} \ar@/^{6pc}/[rrruu]_{1\otimes \id_{\UU_n \fg}} &&&
%{\frak Z}_{E_n}(\UU_n g) \otimes \UU_n \fh \ar[rd]^{\ev_{\UU_n h}}  &\\
%&& \UU_n \fh \ar[rr]^{\UU_n g} \ar[ur]^{1\otimes \id_{\UU_n \fh}} && \UU_n \fl .}
%commutative (since $\UU_n (g\circ f) = \UU_n g\, \circ \, \UU_n f $;  the commutativity of the lower part of the diagram being by definition of centralizers).
%By Theorem~\ref{thm:centralizerfactorization}, we know that the factorization algebras models for the centralizers are given by the respective Chevalley-Eilenberg cochain factorizations algebras 
